---
title: "ER01-quicksort-Report"
output: html_document
---
Introduction
============


Method
======
We used the algorithm from the link:
http://mescal.imag.fr/membres/arnaud.legrand/teaching/2013/M2R_EP_archive_quicksort.tgz

First, we used the following machine:
Dell Latitude E6400, with 4 GB RAM and two cores.

Results
=======
Loading the measurements, first for 10 threads, then for 2 and 4, for the same data.
```{r, echo=FALSE}
library(ggplot2)
df <- read.csv("./data/measurements_10_T.csv")
df2 <- read.csv("./data/measurements_2_4_6_8_T.csv")
df3 <- read.csv("./data/measurementsRANDOM_par.csv")
```

Compute the average execution time for each size and type.

```{r}
library(plyr)
df_avg <- ddply(df,c("Size","Type"), summarise, Time = mean(Time))
df2_avg <- ddply(df2,c("Size","Type","Cores"), summarise, Time = mean(Time))
df3_avg <- ddply(df3,c("Size","Type"), summarise, Time = mean(Time))
```


```{r}
par(mfrow=c(2,2))
```

Plotting the execution time for different types with different number of threads.
```{r}
ggplot(data=df3_avg,aes(x=Size,y=Time,color=Type))+geom_line() + geom_vline(xintercept = 5E04)

```

Speedup

```{r}
seq <- df2_avg[df2_avg$Type == " Sequential",]
par2 <- df2_avg[df2_avg$Type == " Parallel (2)",]
par4 <- df2_avg[df2_avg$Type == " Parallel (4)",]
par6 <- df2_avg[df2_avg$Type == " Parallel (6)",]
par8 <- df2_avg[df2_avg$Type == " Parallel (8)",]
par2_speedup <- par2
par2_speedup["Time"] <- seq["Time"] / par2_speedup["Time"]
par4_speedup <- par4
par4_speedup["Time"] <- seq["Time"] / par4_speedup["Time"]
par6_speedup <- par6
par6_speedup["Time"] <- seq["Time"] / par6_speedup["Time"]
par8_speedup <- par8
par8_speedup["Time"] <- seq["Time"] / par8_speedup["Time"]

df2_speedup <- rbind(par2_speedup, par4_speedup, par6_speedup, par8_speedup, seq)

ggplot(data=df2_speedup, aes(x=Cores,y=Time,color=Size, group = Size))+ geom_point() + geom_line()
```
ggplot(data=df2_avg,aes(x=Cores,y=Time,color=Size, group = Size))+ geom_point() + geom_line() + geom_vline(xintercept = 1E1)

